### 2021-10-06 test/lambdapure/compile/bench/speedup-rgn.tex
checkpoint rgn stuff

\definecolor{color0}{rgb}{0.847058823529412,0.105882352941176,0.376470588235294}
\definecolor{color1}{rgb}{0.984313725490196,0.603921568627451,0.6}

\begin{axis}[
legend cell align={left},
legend columns=100,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, at={(1,1.3)}, draw=none},
tick align=outside,
tick pos=left,
x grid style={white!69.0196078431373!black},
xmin=-0.72, xmax=8.52,
xtick style={color=black},
xtick={0,1,2,3,4,5,6,7,8},
xticklabel style={rotate=15.0},
xticklabels={
  binarytrees-int,
  binarytrees,
  const\_fold,
  deriv,
  filter,
  qsort,
  rbmap\_checkpoint,
  unionfind,
  geomean
},
y grid style={white!69.0196078431373!black},
ylabel style={rotate=-90.0},
ylabel={Speedup over λpure simplifier},
ymin=0, ymax=1.2075,
ytick style={color=black}
]
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.1,1.15);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0}
\addlegendentry{rgn simplifier}

\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.9,1);
\draw[draw=none,fill=color0] (axis cs:1.7,0) rectangle (axis cs:1.9,0.92);
\draw[draw=none,fill=color0] (axis cs:2.7,0) rectangle (axis cs:2.9,0.86);
\draw[draw=none,fill=color0] (axis cs:3.7,0) rectangle (axis cs:3.9,0.99);
\draw[draw=none,fill=color0] (axis cs:4.7,0) rectangle (axis cs:4.9,1);
\draw[draw=none,fill=color0] (axis cs:5.7,0) rectangle (axis cs:5.9,0.99);
\draw[draw=none,fill=color0] (axis cs:6.7,0) rectangle (axis cs:6.9,1.01);
\draw[draw=color1,fill=color1] (axis cs:7.7,0) rectangle (axis cs:7.9,0.99);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:-0.1,0) rectangle (axis cs:0.1,1.12);
\addlegendimage{ybar,ybar legend,draw=none,fill=white!61.9607843137255!black}
\addlegendentry{none}

\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:0.9,0) rectangle (axis cs:1.1,1);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:1.9,0) rectangle (axis cs:2.1,0.92);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:2.9,0) rectangle (axis cs:3.1,0.98);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:3.9,0) rectangle (axis cs:4.1,1.03);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:4.9,0) rectangle (axis cs:5.1,1.02);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:5.9,0) rectangle (axis cs:6.1,0.99);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:6.9,0) rectangle (axis cs:7.1,1);
\draw[draw=white!79.2156862745098!black,fill=white!79.2156862745098!black] (axis cs:7.9,0) rectangle (axis cs:8.1,1.01);
\draw (axis cs:-0.3,1.15) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{1.15};
\draw (axis cs:0.7,1) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:1.7,0.92) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{0.92};
\draw (axis cs:2.7,0.86) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{0.86};
\draw (axis cs:3.7,0.99) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{0.99};
\draw (axis cs:4.7,1) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:5.7,0.99) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{0.99};
\draw (axis cs:6.7,1.01) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:7.7,0.99) ++(0pt,1pt) node[
  scale=0.4165,
  anchor=south,
  text=black,
  rotate=0.0
]{0.99};
\end{axis}

>>>>

\definecolor{color0}{rgb}{0.847058823529412,0.105882352941176,0.376470588235294}

\begin{axis}[
legend cell align={left},
legend columns=100,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, at={(1,1.3)}, draw=none},
tick align=outside,
tick pos=left,
x grid style={white!69.0196078431373!black},
xmin=-0.32, xmax=0.12,
xtick style={color=black},
xtick={0},
xticklabel style={rotate=15.0},
xticklabels={binarytrees-int},
y grid style={white!69.0196078431373!black},
ylabel style={rotate=-90.0},
ylabel={Speedup over no simplifier},
ymin=0, ymax=1.0395,
ytick style={color=black}
]
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.1,0.87);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0}
\addlegendentry{λpure over none}

\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:-0.1,0) rectangle (axis cs:0.1,0.99);
\addlegendimage{ybar,ybar legend,draw=none,fill=white!61.9607843137255!black}
\addlegendentry{rgn over none}

\draw (axis cs:-0.3,0.87) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{0.87};
\end{axis}
